Meta-analysis

### 2020-06-23 04_MetaAnalysis.Rmd
Remove lmer analysis and variance imputation

First let's compare models with and without a log transformed response variable to evaluate if the log transformed model better fits our assumptions of normality.
Next we will test whether including `spray_management` as a fixed effect variable significantly accounts for enough variation to be included in the model.
Finally we will test whether including `spray_management`  as a random slope significantly accounts for enough variation to be used in the model.

```{r LME_slimmer_cluster_disease_mod}
m8 <- lmer(grain_yield.t.ha * 1000 ~ factor(spray_management) +
              (factor(spray_management) | trial),
           data = slimmer_PM_dat)

m9 <- lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
              (factor(spray_management) | trial),
           data = slimmer_PM_dat)

m10 <- lmer(log(grain_yield.t.ha * 1000) ~
               (factor(spray_management) | trial),
            data = slimmer_PM_dat)

m11 <-
   lmer(log(grain_yield.t.ha * 1000) ~ factor(spray_management) +
           (1 | trial),
        data = slimmer_PM_dat)
```

```{r m8_vs_m9}
anova(m8, m9) # m9 is significantly better model
```
There is a significant difference between `m8` and `m9`, with `m9` showing the best fit and lowest AIC: `r min(anova(m8, m9)$AIC)`.

```{r m9_vs_m10}
anova(m9, m10) # m9 is significantly better model
```

There is a significant difference between `m10` and `m9`, with `m9` showing the best fit and lowest AIC: `r min(anova(m9, m10)$AIC)`.

```{r m9_vs_m11}
anova(m9, m11) # m11 is a simpler model which is no different to m9
```

There is no difference between the models, which means the the simpler model `m11` is the better model, also making it the best model from the four above with the lower AIC of -`r min(anova(m9, m11)$AIC)`).

```{r}
summary(m11)
```

This linear mixed effect model shows:

   - A single `early` spray before first sign of powdery mildew is not likely to increase yields.

   - One spray at the `recommended` timing, or two sprays starting at the `recommended` first spray, are likely to produce significantly higher grain yields compared to the no spray control.

   - The `Late_plus` spray which has one or more follow-up sprays after first sign are likely to increase the mean grain yield.

   - `Recommended_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control. However showed no difference to either the `recommended` or `Late_plus` treatments.

#### Imputing sample variances from Mean squares

```{r imputing_MSE_dataSpread, eval=FALSE, include=FALSE}
slimmer_PM_dat <- read.csv("cache/slimmer_PM_clusterdat.csv")
hist_usq(unique(slimmer_PM_dat$Y_Msquare))
hist_usq(log(unique(slimmer_PM_dat$Y_Msquare))) # log mean square has a more normal distribution
```

Imputing using a log transformation of the data is required.
Which trials need variance imputation?

```{r imputing_MSE, eval=FALSE, include=FALSE}
TrialMSQ <- slimmer_PM_dat %>%
   group_by(trial_ref, location, year) %>%
   summarise(unique(Y_Msquare))

TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`), c("trial_ref", "location","year")]
```

```{r imputation_MSE, eval=FALSE, include=FALSE}
for (i in TrialMSQ[is.na(TrialMSQ$`unique(Y_Msquare)`),]$trial_ref) {
   slimmer_PM_dat[slimmer_PM_dat$trial_ref == i, "Y_Msquare"] <-
      exp(rnorm(
         n = 1,
         mean = mean(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE),
         sd(log(TrialMSQ$`unique(Y_Msquare)`), na.rm = TRUE)
      ))
}
```

The use of these imputed MSE was giving a varied outcome each time it was run. 
The next code chunk removes the studies without variation, given we can't reliably impute them.

```{r remove_yieldErrorNAs}
slimmer_PM_dat <- 
   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error),]
```

@@

@@

>>>>

@@

First lets remove any entries missing variance.

@@

slimmer_PM_dat <- 
   slimmer_PM_dat[!is.na(slimmer_PM_dat$yield_error),]
